\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}

\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}

\newenvironment{solution}{\color{blue}\textit{Solution.}}{\color{black}}

\begin{document}
\begin{center}
    \begin{large}
        \textbf{Assignment 6} \\
        MAA4211 \\
        Carson Mulvey
    \end{large}
\end{center}

\begin{enumerate}
    \item[\textbf{(Graded) 2.7.3.}]
    For both proofs, it suffices to show (i), as (ii) is immediately implied by the contrapositive.
    \begin{enumerate}
        \item Suppose $\sum_{k=1}^\infty b_k$ converges. Let $\epsilon > 0$. Then there exists and $N \in \N$ such that for $n>m \geq N$, we have
        \[
            |b_{m+1} + b_{m+2} + \cdots + b_n| < \epsilon.
        \]
        However, because $0 \leq a_k \leq b_k$ for all $k \in \N$, we can sum these inequalities to show that $a_{m+1}+a_{m+2}+\cdots + a_n \leq b_{m+1} + b_{m+2} + \cdots + b_n$. Because these quantities are positive, this implies
        \begin{align*}
            |a_{m+1}+a_{m+2}+\cdots + a_n| &\leq |b_{m+1} + b_{m+2} + \cdots + b_n| < \epsilon.
        \end{align*}
        Thus, taking the same $N$ as picked for $(b_n)$, we can apply the Cauchy Criterion for Series again, showing that $\sum_{k=1}^\infty a_k$ converges.

        \item Let $(s_k)$ and $(t_k)$ be the sequences of partial sums of $(a_k)$ and $(b_k)$, respectively. Because all terms of $(a_k)$ and $(b_k)$ are positive, both $(s_k)$ and $(t_k)$ are increasing sequences.
        
        Now suppose $\sum_{k=1}^\infty b_k$ converges to $t$. Then, since $(t_k)$ is increasing, $(t_k)$ is bounded by $t$. However, since $a_k\leq b_k$ for all $k\in \N$, we also have $s_k \leq t_k$ for all $k \in \N$. This implies that $(s_k)$ is also bounded by $t$. Thus, $(s_k)$ is monotonic and bounded. By the Monotone Convergence Theorem, it must converge, and hence $\sum_{k=1}^\infty a_k$ also converges.
    \end{enumerate}

\end{enumerate}

\end{document}