\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[dvipsnames]{xcolor}

\newenvironment{solution}{\color{blue}\textit{Solution.}}{\color{black}}

\begin{document}
\begin{center}
    \begin{large}
        \textbf{Homework 1 Revisions} \\
        MAD4204 \\
        Carson Mulvey
    \end{large}
\end{center}

\begin{enumerate}
    \item[2.] Let $G = ([n],E)$ be a finite simple graph.
    Let $M$ be a maximal matching in $G$ and $M'$ be a maximum matching in $G$.
    Prove that $|M'| \leq 2 |M|$.

    \begin{solution}
        Let $V(S)$ denote the set of vertices in at least one edge of set $S\subseteq{E}$. That is, $V(S)=\{v\in{V}:\exists {w}\in{V},(v,w)\in{E}\}$. Then we have $|V(M)|=2|M|$ and $|V(M')|=2|M'|$, since vertices cannot be shared between edges in a matching.

        Suppose that an edge $(v,w)\in{E}$ had $v,w\notin{V(M)}$. Then $(v,w)$ can be added to $M$, which would make $M$ not maximal. Thus, every edge in $E$ has at least one vertex in $V(M)$. But since $M'\subseteq{E}$, every edge in $M'$ must also have at least one vertex in $V(M)$, which would then also be in $V(M')\cup{V(M)}$. It follows that
        \begin{align*}
            |M'|&\leq{|V(M')\cup{V(M)}|} \\
            &\leq{|V(M)|} \\
            &=2|M|
        \end{align*}
        as desired. \qedsymbol{}
    \end{solution}
     
    \item[4.] For $\mathcal{M}$ a matroid on ground set $S$ (from Problem 3, we can define it in terms of bases or independent sets, whichever is more convenient), let $w:S \to \mathbb{R}_{\geq 0}$.
    For $B$ a basis in $\mathcal{M}$, define $w(B) = \sum_{b \in B} w(b)$.
    
    Describe an algorithm for finding the basis $B$ minimizing $w(B)$ and prove that it is optimal.
    
    (Hint: compare to the greedy algorithm for finding the minimum weighted spanning tree)
    
    \begin{solution}
        We will define a matroid in terms of its independent sets, $\mathcal{M}_I$. We can define a greedy algorithm that finds a basis $B$ minimizing $w(B)$ by starting with $B=\varnothing $. We then construct $B$ by continually considering an element $a\in{S}$ with $a\notin{B}$ that minimizes $w(S)$. If $B\cup\{a\}\in{\mathcal{M}_I}$, then we add $a$ to $B$, and otherwise, we don't add $a$ and continue the algorithm. We claim that this is an optimal algorithm.

        We will prove this by contradiction. Assume that the greedy algorithm gives a basis $B$, while the matroid has a basis $A$, where $w(B)>w(A)$. In question 3, it was proven that all matroid bases have the same cardinality, so let $|B|=|A|=n$. Enumerate the elements of $B$ as $b_1,b_2,\dots{},b_n$ and the elements of $A$ as $a_1,a_2,\dots{},a_n$ such that $w(b_1)\leq{w(b_2)}\leq\cdots\leq{w(b_n)}$ and $w(a_1)\leq{w(a_2)}\leq\cdots\leq{w(a_n)}$.

        Since $A$ must eventually reach a smaller weight than $B$, let $i$ be the smallest integer where $\sum_{j=1}^{i}{w(a_j)}<\sum_{j=1}^{i}{w(b_j)}$. We have $i>1$ since $w(b_1)$ is minimal over the whole matroid.

        Since $A$ ``takes over" at $i$, we have $w(a_i)<w(b_i)$. Let $B_{i-1}$ be the independent set formed in the first $i-1$ steps and $A_i$ be the independent set formed in the first $i$ steps. By the augmentation property, since $|B_{i-1}|<|A_i|$, we we have some $a_j\in{A}$ such that $B_{i-1}\cup\{a_j\}$ is an independent set. However, since $j\leq{i}$, $w(a_j)<w(b_i)$, so $b_i$ can't be added at the $i$th step of the algorithm, forming a contradiction. Thus, the algorithm produces a minimal basis.
    \end{solution}

\end{enumerate}    

\end{document}