\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx, nicefrac}
\usepackage{tikz, nicefrac}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\newenvironment{solution}{\color{teal}\textit{Solution.}}{\color{black}}

\begin{document}

%%%Version 1%%%%

\flushleft

\begin{center}
    \begin{large}
        \textbf{Homework 2} \\
        MAD4204 \\
        Carson Mulvey
    \end{large}
\end{center}

\pagestyle{empty}


\flushleft

\begin{enumerate}

\item[2.]
\begin{enumerate}
\item A graph $G = (V,E)$ is \emph{factor critical} if $G - v$ has a perfect matching for every $v \in V$.
Prove no bipartite graph is factor critical.

\begin{solution}
    We will prove by contradiction. Suppose that a bipartite graph $G = (A \sqcup B, E)$ is factor critical. Then, for arbitrary $a\in{A}$ and $b\in{B}$, $G-a$ and $G-b$ each have perfect matchings. Since a bipartite graph with a perfect matching must have equal cardinality between its disjoint sets, $G-a$ and $G-b$ give $|A|-1=|B|$ and $|A|=|B|-1$, respectively, which together form a contradiction. Thus, no bipartite graph is factor critical. \qedsymbol
\end{solution}

\item Let $G = (A \sqcup B, E)$ be a bipartite graph with $|A|= 10, |B| = 12$, $d(a) \leq 4$ for all $a \in A$ and $d(b) = 3$ for all $b \in B$.
Prove that $G$ has a matching of size at least $9$.

\end{enumerate}

\item[3.] Fix $k,n \in \mathbb{N}$ with $k < n/2$.
Let $G = (A \sqcup B, E)$ be the bipartite graph with
\[
A = \binom{[n]}{k}, \quad B = \binom{[n]}{k+1}, \quad E = \{(X,Y): X \in A, Y \in B, X \subseteq Y\}.
\]
Prove that $G$ contains a matching of size $\binom{n}{k} = |A|$.

\textbf{Bonus point:} Construct a perfect matching on $G$.

\begin{solution}
    Using the result from Problem 1, we have a matching of $|A|$ elements iff $|N(S)|\geq{}|S|+|A|-|A|=|S|$ for all subsets $S\subseteq{A}$. An element $a\in{A}$ has $n-k$ elements to add to make an element in $B$, while an element $b\in{B}$ has $k+1$ elements to remove to make an element in $A$. However, $k<n/2$ implies $n-k\geq{}k+1$, so the degree of a vertex in $A$ is always greater than or equal to one in $B$. Thus $|N(S)|<|S|$ is impossible for any subset $S\subseteq{A}$, so we must have $|N(S)|\geq{}|S|$ as desired.
\end{solution}

\end{enumerate}

\end{document}